---
title: SRT411A0-Justin Gourgouvelis
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## Todo #1 Perform calculation, get percentage
```{r}
((2018-2014)/(2014-1984)) * 100
```

## Todo #2 Save answer to variable, erase variable
```{r}
percent=((2018-2014)/(2014-1984)) * 100
rm(percent)
```

## Todo #3 Sum of numbers
```{r}
sum(4,5,8,11)
```

## Todo #4 Plot 100 random numbers
```{r}
plot(rnorm(100))
```

## Todo #5 Open Manual for Square Root Function
```{r}
help(sqrt)
```

## Todo #6 Make sequence from 31 to 61, then display them as both a row and a matrix P and Q
```{r}
p=seq(from=31, to=60, by=1)
q=matrix(p,ncol=5, nrow=6)
p
q
```

## Todo #7 Create new matrix x1,x2,x3 making a data frame with columns a,b,c. Displaying information
```{r}
x1=seq(from=1, to=100, by=1)
x2=seq(from=101, to=200, by=1)
x3=seq(from=201, to=300, by=1)
t= data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```

## Todo #8 Add colors to the graph rgb = red,green,blue. Level of color dependant on number provided
```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))
```

## Todo #9 Take a Sqaure Root of the mean of 100 random numbers
```{r}
sqrt(mean(rnorm(100)))
```

## Todo #10 Create a file tst1.txt and add information to that file. Change the file by calculating values
```{r}
d = data.frame(g = c(3,4,5),h = c(12,43,54))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt",header=TRUE)
d2$g*5
```

## Todo #11 Enter Today's date and date of my birthday this year
```{r}
date1=strptime( c("20190219","20190815"),format="%Y%m%d")
present=c(10,6)
date1
```
## Todo #12 Create a for loop that checks i against a number and performs calculations based on the result
```{r}
vector=seq(from=1, to=100, by=1)
s=c()
for(i in 1:100)
{
  if(vector[i]<5)
  {
    s[i]=vector[i]*5;
  }
  else if(vector[i]>90)
  {
    s[i]=vector[i]*10;
  }
  else
  {
    s[i]=vector[i]*0.1;
  }
}
s
```
## Todo #13 create a function that will take in a value i for calculation
```{r}
fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
}
```